\documentclass[10 pt, letterpaper]{article}

% Packages:
\usepackage[
    ignoreheadfoot, % set margins without considering header and footer
    top=0.9 cm, % separation between body and page edge from the top
    bottom=1 cm, % separation between body and page edge from the bottom
    left=1 cm, % separation between body and page edge from the left
    right=1 cm, % separation between body and page edge from the right
    footskip=1.0 cm, % separation between body and footer
]{geometry} % for adjusting page geometry
\usepackage{titlesec} % for customizing section titles
\usepackage{tabularx} % for making tables with fixed width columns
\usepackage{array} % tabularx requires this
\usepackage[dvipsnames]{xcolor} % for coloring text
\definecolor{primaryColor}{RGB}{0, 0, 0} % define primary color
\usepackage{enumitem} % for customizing lists
\usepackage{fontawesome5} % for using icons
\usepackage{amsmath} % for math
\usepackage[
    pdftitle={Seetharaman Radhakrishnan's CV},
    pdfauthor={Seetharaman Radhakrishnan},
    pdfcreator={LaTeX},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref} % for links, metadata, and bookmarks
\usepackage{changepage} % for one column entries (adjustwidth environment)
\usepackage{hyperref}
% Formatting and layout adjustments
\pagestyle{empty} % no header or footer
\setcounter{secnumdepth}{0} % no section numbering
\setlength{\parindent}{0pt} % no indentation
\setlength{\topskip}{0pt} % no top skip
\setlength{\columnsep}{0.15cm} % set column separation
\pagenumbering{gobble} % no page numbering

\hypersetup{colorlinks=true,
urlcolor=SkyBlue}
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]

\titlespacing{\section}{
    % left space:
    -1pt
}{
    % top space:
    0.3 cm
}{
    % bottom space:
    0.2 cm
} % section title spacing

\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$} % custom bullet points

% New environment for bullet points
\newenvironment{highlights}{
    \begin{itemize}[
        topsep=0.10 cm,
        parsep=0.10 cm,
        partopsep=0pt,
        itemsep=0pt,
        leftmargin=0 cm + 10pt
    ]
}{
    \end{itemize}
}

% Header command for personal details
\newcommand{\header}{
    \begin{center}
        \LARGE \textbf{Seetharaman Radhakrishnan} \\
        \normalsize 
        \text{Data Scientist\textbar Python Developer \textbar AI/ML Engineer}\\ 
        
        \text{Open to Relocation \& Global Opportunities
         \textbar UK Graduate Visa Holder}\\
        \href{mailto:rseetharaman293@gamil.com}{rseetharaman293@gmail.com} \textbar \href{https://seetharamanrs.github.io/github-portfolio/}{Portfolio} \textbar  \href{https://linkedin.com/in/seetharaman-r}{LinkedIn} \textbar \href{https://github.com/Seetharamanrs}{GitHub}\textbar\href{+44 07776293482}{+44 07776293482} \\
        Sheffield, United Kingdom
        \vspace{-0.23cm}
    \end{center}
}

\begin{document}

% Insert Header
\header

% Section: Summary
\section*{Summary}
AI and Machine Learning graduate with strong Python programming, data analysis, and deep learning skills. Proficient in designing and deploying machine learning pipelines, building interactive apps, and integrating APIs. Experienced in NLP, signal processing, and image analysis. Passionate about solving real-world problems through applied AI, with multiple self-driven projects hosted on GitHub.
\vspace{-0.3cm}


% Section: Experience
\section*{Experience}
% \textbf{Sainsbury's - Sheffield, UK }  \hfill {May 2024 - Present} \\ \textit{Online Assistant}
% \vspace{-0.3cm}

% \begin{itemize}

% \item \textbf Ensured order accuracy and quality by selecting and preparing customer orders.
% \vspace{-0.23cm}
% \item \textbf Provided customer-centric service, accommodating specific product requests and fostering teamwork in a fast-paced setting.
% \end{itemize}
% \vspace{-0.23cm}
\textbf{Developer - Sheffield,UK }\hfill {September 2024--Present} \\ AI \& Python Projects
\vspace{-0.2cm}    
\begin{itemize}
\item \textbf Delivered end-to-end Python applications for math utilities, data tools, and games using OOP and Streamlit.
\vspace{-0.3cm}
\item\textbf Deployed CLI and GUI tools for statistics, unit conversion, matrix operations, and cryptography.
\vspace{-0.3cm}
\item \textbf Executed a Student Performance Analytics project with UCI ML dataset, applying Random Forest and Logistic Regression to \vspace{0.1cm}identify academic performance indicators.

\vspace{-0.3cm}
\item\textbf Published well-documented code with Jupyter notebooks and GitHub repositories.
\end{itemize}
\vspace{-0.34cm}
% Section: Education
\section*{Education}
\textbf{Sheffield Hallam University - Sheffield, UK}\hfill{2023-2024} \\ M.Sc.(Artificial Intelligence)- Merit(2:1)  

\textbf{Anna University- Chennai,India}\hfill{2018-2022} \\B.E(Electronics and Communication) - FirstClass Honors  
\vspace{-0.3cm}
\section*{Core Skills}

\begin{itemize}
    \item \textbf{Deployments \& API Development:} Python , REST APIs, CLI \& Streamlit Apps, GitHub workflow
    \vspace{-0.23cm}
    \item \textbf{Machine Learning \& Deep Learning:} Neural networks, generative AI, probabilistic generative models, LLMs.
    \vspace{-0.23cm}
    \item \textbf{Computer Vision \& Image Processing:} AI-driven image reconstruction, content editing, and signal processing.
    \vspace{-0.23cm}
    \item \textbf{Programming \& Frameworks:} Python, TensorFlow, PyTorch, Sklearn, Langchain.
    \vspace{-0.23cm}
    \item \textbf{Model Validation\& Optimization:} Cross-validation, hyperparameter tuning, AUC-ROC, model interpretability
       \vspace{-0.23cm}
    \item \textbf{Data Analysis\& Optimization:} Feature engineering, data preprocessing, statistical analysis, visualization.
    \vspace{-0.23cm}
    \item \textbf{Tools \& Version Control:} Git, Google Colab, VS Code, Webots, Overleaf, MATLAB

\end{itemize}
% Section: Projects
\section*{Projects \textbar \href{https://github.com/Seetharamanrs?tab=repositories} {Link}}
\begin{itemize}
 \item \textbf{SuperStore Sales Dashboard } \hfill{Jun 2025} \\Implemented interactive sales dashboard and forecasting models (Prophet \& ARIMA) on Superstore dataset; reduced load time from \textbf{0.40s to 0.01s} using data caching and enabled real-time exploration with filters, KPIs, and visual insights.



    \vspace{-0.23cm}
     \item \textbf{Student Performance Analytics}\hfill{Jun 2025} \\Machine learning models were enhanced to predict student grades, improving accuracy from \textbf{91\% to 92\%} through hyperparameter tuning and feature selection. Key factors influencing performance were identified, enhancing model interpretability and decision-making support.

    \vspace{-0.23cm}
    \item\textbf{Math Utility Toolkit }\hfill{ May 2025}\\ Crafted a modular Python toolkit integrating calculator, geometry, statistics, and sequence generators with CLI and Streamlit GUI interfaces. Organized ~1000 lines of code using OOP principles to ensure scalability and maintainability. Validated functionality with \textbf{25\texttt{+}} test cases, enhancing accessibility to essential mathematical tools..
   % \vspace{-0.15cm}
   %  \item\textbf{Python Utility Toolkit}\hfill{ May 2025}\\ Created a multi-functional Python command-line tool featuring unit conversion, cipher encryption/decryption, random number games, scientific and matrix calculators, and age/date utilities using modular classes and libraries such as {python-dateutil} ,{streamlit} and  {NumPy}.    
   % \vspace{-0.15cm}
   %  \item \textbf{Reconstructing Image from Brain Activity}\hfill{ Jan 2024}\\Applied deep learning in PyTorch to reconstruct images using autoencoders from neural data.

   %  \vspace{-0.15cm}
% \item \textbf{Handwritten Digit Recognition}\hfill{Dec 2023} \\ Developed classification model using Random Forest and neural networks with TensorFlow, Sklearn, NumPy, and Pandas.
%     \vspace{-0.15cm}
%         \item \textbf{Wall Following E-puck Robot}\hfill{ Dec 2023} \\Designed autonomous navigation algorithms leveraging sensor fusion and Webots simulation.
%     \vspace{-0.15cm}
 \vspace{-0.23cm}
    \item \textbf{Schwa Identification}\hfill{ May 2024}\\ Collaborated with client to implement AI-driven speech pipeline for ESOL pronunciation, focusing on schwa features and delivering precise phonetic feedback beyond word-level analysis.
    \vspace{-0.23cm}
    \item \textbf{Forecasting Depression in Students}\hfill{ Sept 2024}\\ Implemented ML models (Random Forest, SVM, Neural Networks) to predict student depression severity. Achieved \textbf{95.06\%} accuracy and \textbf{0.995 }AUC-ROC using feature selection \textbf{(threshold= 0.2)} and cross-validation. Identified key factors such as academic stress and social isolation to support early mental health intervention.
    \vspace{-0.23cm}
    % \item \textbf{Heart Diseases Prediction}\hfill{Dec 2023} \\ Designed a predictive analytics system using KNN and Random Forest, incorporating feature engineering and data preprocessing.
    
\end{itemize}

% Section: Core Skills

\vspace{-0.1cm}
% Section: Certifications
\section*{Certifications}
\begin{itemize}
    \item\textbf{Python for Data Science, AI \& Development}(IBM-Coursera) \hfill {Feb 2025}
    \vspace{-0.23cm}
    \item\textbf{Building a Personalized Chatbot with OpenAI and LangChain}(LinkedIn) \hfill Feb 2025  
       \vspace{-0.23cm}
 
    \item\textbf{Hands-On AI: Build a Generative Language Model from Scratch}(LinkedIn)\hfill Dec 2024
    \vspace{-0.25cm}
    \item \textbf{Generative AI: Working with Large Language Models}(LinkedIn) \hfill March 2024
    \vspace{-0.25cm}
    \item \textbf{Introduction to Large Language Models}(LinkedIn) \hfill Mar 2024 
       \vspace{-0.25cm}
    \item \textbf{Signal Processing Onramp}(MATLAB Coding) \hfill {Mar2024}
       \vspace{-0.25cm}
    \item\textbf{MySQL for Non-Programmers}(LinkedIn) \hfill {Nov 2024} 
     \vspace{-0.25cm}
\end{itemize}


% \section{Additional Information}
% \begin{itemize}
%     \item \textbf{Visa Status:} { Eligible to work full-time in the UK under the Graduate Route Visa (valid until Dec 2026)}
%     \item \textbf{Open to Relocation:} open to relocate and remote opportunities
% \end{itemize}







\end{document}



Technical Skills
Programming Languages: Python, Java, C++

Machine Learning & AI: Neural Networks, Deep Learning, Generative AI, Random Forest, KNN, Transformers

Computer Vision & Image Processing: Autoencoders, Signal Processing, Image Reconstruction

Frameworks & Libraries: TensorFlow, PyTorch, Scikit-learn, NumPy, Pandas, LangChain

Tools & Version Control: Git, Google Colab, VS Code, Webots, Overleaf, MATLAB

Database Management: MySQL